---
title: "WUP_04"
author: "Candice Fallon"
date: "Spring 2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
scores <- read.csv(file = "GSScsv.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

Each person whose data was collected for the dataset "scores" is a "case". We will compare DEGREE, a factor variable describing the highest scholastic degree obtained by a case, with WORDSUM describing the case's score on the WRODSUM test. A boxplot will show the distribution of WORDSUM scores in each category, or factor. A numerical summary will tell us the average, or mean, score as explained by each factor. If differences seem significant enough, Tukey will be used to compare the factors in pairs.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
basicCN <- ggplot(scores,aes(x=DEGREE,y=WORDSUM))

basicCN + geom_boxplot(notch= FALSE ,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="DEGREE vs WORDSUM scores")
```

Clearly, the scores from LT High School are much lower than the other scores(except for High School). High School is similar in this respect, but its scores seem more varied. For the most part, graduates had higher scores than any other factor/ category; the bottom of the Graduate box doesn't even reach the top of the High School and LT High School boxes.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
